\documentclass[margin,line]{res}
\usepackage{pifont}
\usepackage[mathtimes]{ttfshape}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
pdfstartview={FitBH}
}
%\DeclareTTFiles{Pala}{pala.ttf}{palai.ttf}{palab.ttf}{palabi.ttf}

%\usepackage{times}
%\usepackage[T1]{fontenc}
\usepackage{palatino}

%\pagestyle{empty}
%\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}
\textwidth=145mm       %-- A4
\textheight=254mm      %-- A4
\oddsidemargin -15mm \evensidemargin -15mm

%\setlength{\parindent}{0in} \setlength{\parskip}{0in}
%\setlength{\itemsep}{0in} \setlength{\topsep}{0in}
%\setlength{\tabcolsep}{0in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments
\definecolor{bg}{gray}{0.85}

\renewcommand{\sectionfont}{\fontfamily{Pala}\selectfont}
% A ressection is a main section (<H1>Section</H1>)
\newcommand{\ressection}[1]{
    {\colorbox{bg}{\fontfamily{phv}\selectfont\large#1}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}
%\TTFPala
%\fontfamily{ppl} \selectfont

\name{{\fontfamily{phv}\selectfont\Huge\scshape Zhichun Wu}}

\begin{resume}
 \hspace{-1cm}
\begin{minipage}{1\linewidth}
  \begin{minipage}{0.49\linewidth}
    Room 415, Building 36 of Student Flats, \\
    New Campus of Fuzhou University \\
    Minhou, Fuzhou, Fujian, 350108, P.R.China \\
  \end{minipage}%
  \hspace{\fill}%
  \begin{minipage}{0.49\linewidth}%
    {\Large\ding {37}}Phone: (86) 15806021944 \\
    {\Large\ding {41}}Email: {\tt wzc1989@gmail.com} \\
  \end{minipage}
\end{minipage}

\section{\ressection{Education}}

\section{\em 9/2007 -- Present}
\textbf{B.E.\  in Software Engineering} \newline
 Fuzhou University, Fujian, China
 \newline
 (expected graduation date, July 2011)

\section{\ressection{Research Interest}}
\vspace{1cm}
\begin{itemize}
\item[\ding {52}] Design and Analysis of Algorithms and  Data Structures
\end{itemize}

\section{\ressection{Course Design}}
\vspace{1cm}
\section{\em 6/2009}
\textbf{Simple Research on Source-Code Similarity Detection}\\
One of our semester assignments of C++ Programming course is implementing
an simple version of source code similarity detection program. I just prepare a keyword list and count each concerned keyword occurrences.
Then use some experienced formula to evaluate the similarity.

\section{\em 1/2010}
\textbf{Mini Library Management System based on PHP, MYSQL, APACHE}\\
It is what I choose for our Datebase course's final assignment. I implement an mini library
management using simple php and a little js and css. I use mysql to store data, apache to run the system.
I just create one php file for each webpage, no MVC involved.

\section{\em 3/2010 -- 6/2010}
\textbf{Online Examination System}\\
It is our team project for Software Engineering course. It aims at saving time and effort for teachers by carrying out examinations online.
I participate in database design and some server side programming.

\section{\ressection{Extra-Curriculum Activities}}
\vspace{5mm}
\section{\em 8/2008 -- Present} member of \textbf{ACM International Collegiate
Programming Contest} of Fuzhou University\vspace{-5mm}
\section{\em 11/2010} \textbf{Problem Setter} of $35$th ACM/ICPC Asia Regional Contest Fuzhou Site \textbf{Warm Up} Contest\vspace{-5mm}
\section{\em 11/2010} \textbf{Problem Setter} of $35$th ACM/ICPC Asia Regional Contest Fuzhou Site Online Contest\vspace{-5mm}
\section{\em 8/2008 -- Present} Attending various of Algorithm Programming Contest(icpc/topcoder/codejam..etc).\\
 My Topcoder handle is \href{http://www.topcoder.com/tc?module=MemberProfile&cr=22758532}{code6}.

\section{\ressection{Awards}}
\vspace{5mm}
\section{\em 10/2009} \textbf{Silver Medal} , $34$th ACM International
Collegiate Programming Contest, Asia, Hefei\vspace{-5mm}

\section{\em 10/2009} \textbf{Gold Medal} , $34$th ACM International
Collegiate Programming Contest, Asia, Shanghai\vspace{-5mm}

\section{\em 2/2010} \textbf{Honorable Mention} , $34$th ACM International
Collegiate Programming Contest \textbf{World Finals}\vspace{-5mm}

\section{\em 7/2010} \textbf{Final Standing} , 2010 Baidu Astar\vspace{-5mm}

\section{\em 10/2010} \textbf{Gold Medal} , $35$th ACM International
Collegiate Programming Contest, Asia, Hangzhou

\section{\ressection{Skills and Strength}}
\vspace{1cm}
\begin{itemize}
            \item[\ding {72}] Main Languages: C, C++
            \item[\ding {72}] Other Languages: PHP, Java
            \item[\ding {72}] Operating Systems: Windows XP, Linux
\end{itemize}

\end{resume}

\end{document}
